---
title: "p8105_hw1_ws2721"
author: "WooJin Shin"
date: "2024-09-18"
output: github_document
---

Problem 1
------------------------------------------------------------
```{r include=FALSE}
data("penguins", package = "palmerpenguins")
```
Pulling the data

```{r eval = FALSE}
library(skimr)
skimr::skim(penguins)
```

This works and gives the information I need, but I could do more.

```{r}
summary(penguins)
```

This summary gives us the information of the data.

This data shows the sex, bill length, bill depth, flipper length and body mass among 3 species (Adelie, Chinstrap, Gentoo) in 3 islands (Biscoe, Dream, Torgersen) during the time period between 2007 and 2009.

There are 2 NA's in bill length, bill depth, flipper length, and body mass.

There are 11 NA's in sex.


```{r}
head(penguins)
nrow(penguins)
ncol(penguins)
mean(penguins[["flipper_length_mm"]], na.rm = TRUE)
```

According to `head(penguins)` and `nrow(penguins)` and `ncol(penguins)`:

There are total of 344 rows and 8 columns, which means there are 344 observations and 8 variables.

There are 8 variables consist of 3 factor variable type, 3 integer variable type and 2 double variable type.

3 factor variables are "species", "island", and "sex".

3 integer variables are "flipper_length_mm", "body_mass_g", and "year".

2 double variables are "bill_length_mm" and "bill_depth_mm".

The mean of flipper length is 200.9152, with 2 values missing and not included.

```{r}
library(ggplot2)
ggplot(penguins, aes(y = flipper_length_mm, x = bill_length_mm, color = species)) + geom_point(na.rm = TRUE)
```

Removed 2 missing values from flipper_length and bill_length.

```{r message= FALSE}
ggsave(filename = "penguins.pdf")
```

scattor plot saved

Problem 2
------------------------------------------------------------

```{r echo = FALSE}
library(tidyverse)
```

```{r}
p2_df = tibble(
  rsamp = rnorm(10),
  log_vec = rsamp > 0,
  char_vec = c("H","E","L","L","O","W","O","R","L","D"),
  fac_vec = c("lvl1","lvl2","lvl3","lvl1","lvl2","lvl3","lvl2","lvl2","lvl3","lvl3")
)
```

Data entry:
Created the data frame called `p2_df` that includes a random sample of size 10 from a standard Normal distribution, logical vector indicating whether elements of the sample are greater than 0, character vector of length 10, and a factor vector of length 10, with 3 different factor “levels”.

```{r}
mean(pull(p2_df,rsamp))
mean(pull(p2_df,log_vec))
mean(pull(p2_df,char_vec))
mean(pull(p2_df,fac_vec))
```

The character vector and factor vector gives NA, which means that the can't calculate the average because it is not numeric or logical. Numeric vectors come out as numbers and logical vectors come out as 1 `TRUE` or 0 `FALSE` that could be used to calculate the mean that will approximate to 0.5. 



```{r eval = FALSE}
p2_df |>
  mutate(
    rsamp = as.numeric(rsamp),
    log_vec = as.numeric(log_vec),
    char_vec = as.numeric(char_vec),
    fac_vec = as.numeric(fac_vec)
  )
```

When converting the each data set to numeric values:

1. The values in `rsamp` correctly shows their numbers.

2. The values in `log_vec` becomes 1 and 0.

3. The values in `char_vec` becomes NA because the character cannot be converted to numbers.

4. The values in `fac_vec` becomes NA because the factor vector cannot be converted to numbers as well.

Since `char_vec` and `fac_vec` cannot be converted to numbers, we can't get the mean. It explains what is happening when we are trying to take the mean.