---
title: "p8105_hw1_ws2721"
author: "WooJin Shin"
date: "2024-09-18"
output: github_document
---

**Problem 1**

```{r}
data("penguins", package = "palmerpenguins")
```
Pulling the data

```{r eval = FALSE}
library(skimr)
skimr::skim(penguins)
```

This works and gives most of the information I need, but I could do more.

```{r}
summary(penguins)
```

This summary gives us the information of the data.

This data shows the sex, bill length, bill depth, flipper length and body mass among 3 species (Adelie, Chinstrap, Gentoo) in 3 islands (Biscoe, Dream, Torgersen) during the time period between 2007 and 2009.

There are 2 NA's in bill length, bill depth, flipper length, and body mass.

There are 11 NA's in sex.


```{r}
head(penguins)
nrow(penguins)
ncol(penguins)
mean(penguins[["flipper_length_mm"]], na.rm = TRUE)
```

According to `head(penguins)` and `nrow(penguins)` and `ncol(penguins)`:

There are total of 344 rows and 8 columns, which means there are 344 observations and 8 variables.

There are 8 variables consist of 3 factor variable type, 3 integer variable type and 2 double variable type.

3 factor variables are "species", "island", and "sex".

3 integer variables are "flipper_length_mm", "body_mass_g", and "year".

2 double variables are "bill_length_mm" and "bill_depth_mm".

The mean of flipper length is 200.9152, with 2 values missing and not included.

```{r}
library(ggplot2)
ggplot(penguins, aes(y = flipper_length_mm, x = bill_length_mm, color = species)) + geom_point(na.rm = TRUE)

ggsave(filename = "penguins.pdf")
```

Removed 2 missing values from flipper_length and bill_length.


**problem 2**



